descriptive_Clusters

### 2020-12-11 src/descriptive_Clusters.Rmd
updates in text, tables, figures

@@

UpCluster <- ggplot(cluster.up, aes(help.date.time, mean.up, 
UpCluster + geom_line() + labs(x = "Weekdays March-May") + 

@@

>>>>

#create time variation plots for speedtests for each year
Tests19 <- count(TS2019, date)
TS2019 <- left_join(TS2019, Tests19)
names(TS2019)[13] <- "test frequency 2019"
time.var.plot2019 <- timeVariation(TS2019, pollutant = "test frequency 2019", statistic = "mean")
Tests20 <- count(TS2020, date)
TS2020 <- left_join(TS2020, Tests20)
names(TS2020)[13] <- "test frequency 2020"
time.var.plot2020 <- timeVariation(TS2020, pollutant = "test frequency 2020", statistic = "mean")

#export time variation plots for paper
out.plot <- paste(path, "/paper/v1/figures/time.var.plot2019.png", sep = "")
png(out.plot)
time.var.plot2019
dev.off()

out.plot <- paste(path, "/paper/v1/figures/time.var.plot2020.png", sep = "")
png(out.plot)
time.var.plot2020
dev.off()

@@

UpClusterL <- ggplot(cluster.up, aes(help.date.time, mean.up, 
                                      colour = clusterID)) +
  theme_minimal() +
  geom_line() + 
  labs(x = "Weekdays March-May", y = "mean upload speed", col = "Cluster ID") + 

@@

                     c("Mon", "Tues", "Weds", "Thurs", "Fri")) + 
  geom_point() +
  theme(legend.position = c(0.7, 0.08),
        legend.direction = "horizontal")

#export UpClusterL plot for paper
out.plot <- paste(path, "/paper/v1/figures/UpClusterL.png", sep = "")
png(out.plot)
UpClusterL
dev.off()

#plot next 6 smaller clusters, but exclude 2 clusters with 1 LAD and under 100k pop
cluster.upS <- TS2020 %>%
  group_by(cluster.up, weekday, hour) %>%
  summarise(mean.up = mean(speedup))
names(cluster.upS)[1] <- "clusterID"
names(LAD.cluster.up)[1] <- "clusterID"
cluster.upS <- left_join(cluster.upS, LAD.cluster.up)
cluster.upS <- cluster.upS[which(cluster.upS$up.LADs < 10 & cluster.upS$up.LADs > 1),]
cluster.upS$clusterID <- as.factor(cluster.upS$clusterID)
#add fake dates for plotting
help.dates <- tibble(help.date.time = c(
  make_datetime(year = 2020, month = 3, day = 2),
  make_datetime(year = 2020, month = 3, day = 3),
  make_datetime(year = 2020, month = 3, day = 4),
  make_datetime(year = 2020, month = 3, day = 5),
  make_datetime(year = 2020, month = 3, day = 6)),
                     weekday = c("Mon", "Tue", "Wed", "Thu", "Fri"))
cluster.upS <- merge(cluster.upS, help.dates, by = "weekday")
cluster.upS$hour <- paste(cluster.upS$hour, ":00", sep="")
cluster.upS$help.date.time <- with(cluster.upS, as.POSIXct(paste(help.date.time, hour), format="%Y-%m-%d %H:%M"))
#plot cluster statistic for mean upload speed
UpClusterS <- ggplot(cluster.upS, aes(help.date.time, mean.up, 
                                      colour = clusterID)) +
  theme_minimal() +
  geom_line() + 
  labs(x = "Weekdays March-May", y = "mean upload speed", col = "Cluster ID") + 
  scale_x_datetime(breaks = as.POSIXct(c("2020-03-02 15:00:00", 
                    "2020-03-03 15:00:00", "2020-03-04 15:00:00",
                    "2020-03-05 15:00:00", "2020-03-06 15:00:00"), 
                    labels = "%a"), labels = 
                     c("Mon", "Tues", "Weds", "Thurs", "Fri")) + 
  geom_point() +
  theme(legend.position = c(0.8, 0.08),
        legend.direction = "horizontal")

#export UpClusterS plot for paper
out.plot <- paste(path, "/paper/v1/figures/UpClusterS.png", sep = "")
png(out.plot)
UpClusterS
dev.off()
